Nilpotent Invariants \\ for Generic Discrete Series of Real Groups

### 2024-10-04 whittaker.tex
Removed the date because arXiv adds one
Done?

\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams\footnote{University of Maryland \& IDA Center for Computing Sciences ; \url{jda@math.umd.edu}} {} \& Alexandre Afgoustidis\footnote{CNRS \& Université de Lorraine, Nancy \& Metz ; \url{alexandre.afgoustidis@math.cnrs.fr}}}
%\email{alexandre.afgoustidis@math.cnrs.fr}

@@

By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the Weyl chamber of its Harish-Chandra parameter. 
The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
using some geometric facts.

@@

Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of the Harish-Chandra parameter~$H$ of some generic discrete series representation. Since the Harish-Chandra parameters for discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$. Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ whose Harish-Chandra projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$. By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.

@@

Finally, let us check Proposition \ref{p:Kostant}, 
which says $\Wh(\pi)=\w_X\Leftrightarrow \K(X)\cap\O_\pi\ne \emptyset$. 
Assume $k>0$. Then 
$$
\Wh(\pi(\lambda_{ik}))=G(\R)\cdot(-E_\R^*).
$$
On the other hand, we can compute
$$
\begin{aligned}
\K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*)))\\
&=\psi_c(\K( -\frac 1cF_\R)).\end{aligned}$$
This contains
$$ \psi_c\left(\frac 1c(-F_\R-E_\R)\right)=\psi_c(\frac 1cH_\theta)=2H_\theta^*.
$$
So we do have
$$
\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset\quad (k>0).
$$
The case $k<0$ is similar; in that case we conclude
$\Wh(\pi_{\lambda_ik})=G(\R)E_\R^*$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.

>>>>

\title{Nilpotent Invariants \\ for Generic Discrete Series of Real Groups}
\author{Jeffrey Adams\footnote{University of Maryland \& IDA Center for Computing Sciences ; \url{jda@math.umd.edu}} {} \& Alexandre Afgoustidis\footnote{CNRS \& Université de Lorraine, Nancy \& Metz ; \url{alexandre.afgoustidis@math.cnrs.fr}}}
\date{}

@@

By Lemma \ref{l:pi_to_av} the associated variety of a discrete representation only depends on the $W_K$-orbit of any Weyl chamber containing a representative of its Harish-Chandra parameter. 
The same holds for the wave front set and Whittaker data by Theorem \ref{th:main}. This can also be proved directly 
using some geometric facts.

@@

Now consider the set $\Sigma$ of all points on $\mathcal{S} \cap \mathcal{C}$ which arise as the radial projection of an element~$H$ corresponding to a representative in $\t^\ast$ for the Harish-Chandra parameter of some generic discrete series representation. Since the representatives for Harish-Chandra parameters of discrete series are (a translate of) an integral lattice, the set $\Sigma$ is dense in $\mathcal{S} \cap \mathcal{C}$. Therefore if the open set $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$ is nonempty, there must exist at least one generic discrete series representation~$\pi$ with a Harish-Chandra parameter representative which projects to $\mathcal{S}_\Omega \cap \mathcal{S}_{\Omega'}$. By Lemma~\ref{lem:WF_and_AC} this means $\Omega$ and $\Omega'$ must be contained in $\WF(\pi)$, which implies $\Omega = \Omega'$ since the wavefront set is the closure of a single orbit if $\pi$ is a generic discrete series.

@@

Finally, let us check Proposition \ref{p:Kostant}, 
which says $\Wh(\pi)=\w_X\Leftrightarrow \K(X)\cap\O_\pi\ne \emptyset$. 
Assume $k>0$. Then by~\eqref{e:WF} and Corollary~\ref{cor:matumoto} we have
$$
\Wh(\pi(\lambda_{ik}))=\mathfrak{w}_{-E_\R^*}.
$$
On the other hand, we can compute
$$
\begin{aligned}
\K(-E_\R^*)&=\psi_c(\K(\psi_c\inv(-E_\R^*)))\\
&=\psi_c(\K( -\frac 1cF_\R)).\end{aligned}$$
This contains
$$ \psi_c\left(\frac 1c(-F_\R-E_\R)\right)=\psi_c(\frac 1cH_\theta)=2H_\theta^*.
$$
So we do have
$$
\K(-E_\R^*)\cap G(\R)\cdot 2H_{\theta}^*\ne\emptyset\quad (k>0).
$$
The case $k<0$ is similar; in that case we conclude
$\Wh(\pi_{\lambda_{ik}})=\mathfrak{w}_{E_\R^\ast}$, and $\K(E_\R^*)\cap G(\R)\cdot (-2H_\theta)\ne \emptyset$.
